### 2014-03-26 paper/io.tex

Once objects have been designed and fabricated, the major flexibility for prototyping with pipes stems from the media inserted in them.  The five types of media--gas, liquid, solid, particulate, and threadable--give rise to unique possibilities in output (visual, aural, tactile/haptic, olfactory/gustatory) as well as input (touch/pressure and others).

@@

By crossing pipe types, topologies, and inserted media, we create a space of possible inputs and outputs that can be pipe-mediated.  We offer a table (see Figure \ref{fig:designspace}) containing these possibilities, referencing previous work on input/output techniques where appropriate, noting that many of these techniques have not been attempted using digital fabrication.  We suggest new points in the design space that have been unexplored or not yet explored with digital fabrication.

@@

The physical fabrication process used by different machines gives rise to differing design guidelines.  The two machines we used to create our example objects were the Objet Connex 260 and the Makerbot Replicator 2.

@@

Assembly is easiest on both machines when the model does not require support material.  Models can be ``cut up'' into assembleable pieces to evade support requirements or ease material removal.  We believe that an automatic tool for this task would be highly beneficial, however it is outside the scope of this work.

>>>>

Once objects have been designed and fabricated, the major flexibility for prototyping with pipes stems from the media inserted in them.  The five types of media--gas, liquid, solid, particulate, and threadable--\bjoern{Not just the media in them, but also the systems attached to them to sense changes to chose media or actuate them.

I wonder if you could still push this table yet further back, essentially into the discussion part. So you first show the objects, and then the discussion puts these into context of other work thats been done and provides pointers to future work in other areas of this design space.

}give rise to unique possibilities in output (visual, aural, tactile/haptic, olfactory/gustatory) as well as input (touch/pressure and others).

@@

By crossing pipe types, topologies, and inserted media, we create a space of possible inputs and outputs that can be pipe-mediated.  We offer a table (see Figure \ref{fig:designspace}) containing these possibilities, referencing previous work on input/output techniques where appropriate, noting that many of these techniques have not been attempted using digital fabrication \bjoern{It may be a bit tricky to define what "using digital fab" means here. For example, Harrison 's pneumatically actuated buttons were done on a laser cutter, but also required manual gluing of other layers. Does that count or not?}.  We suggest new points in the design space that have been unexplored or not yet explored with digital fabrication.

@@

\bjoern{The biggest question wrt fabrication for me is - how do I print these cavities? So general support material avoidance or removal strategies should be more prominent.

(I think the lye bath would probably work better than the high pressure water for our objet prints)}
The physical fabrication process used by different machines gives rise to differing design guidelines.  The two machines we used to create our example objects were the Objet Connex 260 and the Makerbot Replicator 2.

@@

Assembly is easiest on both machines when the model does not require support material.  Models can be ``cut up'' \bjoern{This negates some of the benefits compared to other manufacturing techniques.} into assembleable pieces to evade support requirements or ease material removal.  We believe that an automatic tool for this task would be highly beneficial, however it is outside the scope of this work.

### 2014-03-26 paper/limitations.tex

\valkyrie{Our design tool is not yet fully capable of realizing all possibilities in the design space of tubes.  It lacks the network manipulation to make mixing or splitting tubes, unless they are designed in an input vector graphics file.  Future work should also include assisting makers in the fabrication process itself by automatically cutting objects to reduce support material removal issues.  Additionally, as mentioned there are opportunities to improve the algorithm for neon sign routing, as ours does not guarantee a shortest-path routing. --------- this paragraph breaks the latex for some reason?}

>>>>

Our design tool is not yet fully capable of realizing all possibilities in the design space of tubes.  It lacks the network manipulation to make mixing or splitting tubes, unless they are designed in an input vector graphics file.  Future work should also include assisting makers in the fabrication process itself by automatically cutting objects to reduce support material removal issues.  Additionally, as mentioned there are opportunities to improve the algorithm for neon sign routing, as ours does not guarantee a shortest-path routing.

\bjoern{Mention need for a better general 3d routing algorithm for multiple traces }
